\documentclass[a4paper,10.5pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[top=1.4cm, bottom=1.4cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{microtype}
\usepackage{lmodern}
\usepackage{tabularx}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black
}

% ── Colours ──────────────────────────────────────────────────────────────────
\definecolor{accent}{RGB}{13, 71, 161}
\definecolor{techgray}{RGB}{90, 90, 90}

% ── Section headings ─────────────────────────────────────────────────────────
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}
  {0em}
  {}
  [\vspace{-5pt}\textcolor{accent}{\rule{\linewidth}{0.8pt}}\vspace{2pt}]

\titlespacing*{\section}{0pt}{10pt}{4pt}

% ── List settings ─────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.4em,
  itemsep=1.5pt,
  topsep=3pt,
  parsep=0pt,
  label=\textbullet
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{1em}

% ── Helper: job entry ─────────────────────────────────────────────────────────
% Usage: \jobentry{Title}{Date}{Company}{Location}
\newcommand{\jobentry}[4]{%
  \noindent
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} & \textit{#2}\\
    \textit{#3 $\cdot$ #4} & \\
  \end{tabularx}%
  \vspace{1pt}%
}

% ── Helper: tech stack ────────────────────────────────────────────────────────
\newcommand{\techstack}[1]{%
  \vspace{2pt}\noindent{\small\textcolor{techgray}{\textbf{Tech:} #1}}%
}

% =============================================================================
\begin{document}

% ── HEADER ───────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries FAHIM KHAN}\\[4pt]
  {\large\color{accent} Senior Full Stack Engineer}\\[6pt]
  \small
  \href{mailto:fahimkhan20148@gmail.com}{fahimkhan20148@gmail.com}
  \quad$|$\quad
  +971 50 728 6133
  \quad$|$\quad
  \href{https://linkedin.com/in/fahim-khan-232533346}{linkedin.com/in/fahim-khan-232533346}
  \quad$|$\quad
  Abu Dhabi, UAE
\end{center}

\vspace{4pt}

% ── PROFILE ──────────────────────────────────────────────────────────────────
\section{Profile}
Senior Full Stack Engineer with 8+ years of experience architecting high-performance, scalable web applications and real-time systems. Specialist in Rust, TypeScript, and React/Next.js, with a strong track record in fintech (Emirates NBD) and AI/agentic systems. Proven ability to lead engineering teams, establish CI/CD pipelines, and migrate legacy architectures to modern, high-throughput stacks.

% ── CORE COMPETENCIES ────────────────────────────────────────────────────────
\section{Core Competencies}

\begin{multicols}{4}
\noindent
Rust / Go\\
React / Next.js\\
Node.js / NestJS\\
TypeScript

\columnbreak
\noindent
LLMs / AI Agents\\
GraphQL / REST\\
WebSockets / WebRTC\\
Microservices

\columnbreak
\noindent
Docker / Kubernetes\\
AWS (EC2, S3, API GW)\\
PostgreSQL / MongoDB\\
Neo4j

\columnbreak
\noindent
Playwright / Appium\\
CI/CD Automation\\
Ionic / Capacitor\\
Dynatrace
\end{multicols}

% ── WORK EXPERIENCE ──────────────────────────────────────────────────────────
\section{Work Experience}

\jobentry{Full Stack Consultant}{Mar 2025 -- Present}{Presight AI}{Abu Dhabi}
\begin{itemize}
  \item Architected a micro frontend system decoupling deployments across product squads, enabling independent shipping without cross-team bottlenecks.
  \item Built real-time dashboards in React/Next.js using WebSockets and WebRTC to stream live AI inference data with near-zero latency.
  \item Implemented agentic workflows using LLMs, MCP, and tool-calling to automate operational tasks and accelerate legacy code migration.
  \item Maintained backend services in Rust and NestJS, deployed via Docker and Kubernetes on distributed cloud infrastructure.
\end{itemize}
\techstack{Rust $\cdot$ Node.js $\cdot$ NestJS $\cdot$ React $\cdot$ Next.js $\cdot$ TypeScript $\cdot$ Go $\cdot$ GraphQL $\cdot$ Docker $\cdot$ Kubernetes $\cdot$ LLMs $\cdot$ MCP}

\vspace{7pt}
\jobentry{Senior Software Consultant}{Apr 2024 -- Jan 2025}{D4 Insight}{Dubai}
\begin{itemize}
  \item Migrated critical services from Java to Rust, reducing p99 service discovery latency from \textbf{300ms+ to sub-50ms} and cutting infrastructure replicas from \textbf{6 to 3}, halving hosting costs.
  \item Achieved near-zero downtime post-migration --- only one incident in six months, a step-change from pre-migration reliability.
  \item Engineered secure financial dashboards and interbanking API integrations for \textbf{Emirates NBD}, adhering to strict banking security and compliance standards.
  \item Built an HTTP reverse proxy in Rust (Axum/Tokio) for high-concurrency traffic routing with minimal overhead.
  \item Automated API, web UI, and native app testing using Playwright and Appium.
\end{itemize}
\techstack{Rust $\cdot$ Axum $\cdot$ Tokio $\cdot$ Node.js $\cdot$ Angular $\cdot$ MongoDB $\cdot$ Playwright $\cdot$ Appium $\cdot$ Finacle}

\vspace{7pt}
\jobentry{Full Stack Engineer}{Mar 2023 -- Nov 2023}{Egen Solutions Inc}{Remote}
\begin{itemize}
  \item Built a RAG pipeline on GPT-3.5 to automatically migrate legacy Selenium E2E tests to Playwright, cutting the projected timeline from \textbf{1 year to 3 months}.
  \item Led a team of 3 engineers through the migration: daily code reviews, testing standards, and end-to-end delivery ownership.
  \item Architected the Apollo GraphQL federation layer connecting microservices for loan origination, payments, and customer data on the Bridgecrest platform.
  \item Managed AWS infrastructure (EC2, S3, API Gateway) and CI/CD pipelines via GitHub Actions for rapid, reliable releases.
\end{itemize}
\techstack{TypeScript $\cdot$ Angular $\cdot$ Apollo GraphQL $\cdot$ NestJS $\cdot$ Ionic $\cdot$ Playwright $\cdot$ AWS $\cdot$ GitHub Actions $\cdot$ Dynatrace $\cdot$ GPT-3.5}

\newpage
\jobentry{Full Stack Engineer}{Sep 2020 -- Jan 2023}{Segment Hub Technologies}{Mumbai}
\begin{itemize}
  \item Shipped one of the company's first LLM integrations: a GPT-3-powered ``talk to your docs'' interface enabling natural language querying of internal documentation.
  \item Built a high-performance Rust API layer (Axum), significantly reducing server costs while handling concurrent workloads at scale.
  \item Developed cross-platform mobile apps with Ionic/Capacitor for Android and iOS, extending the product beyond Slack.
\end{itemize}
\techstack{Rust $\cdot$ Axum $\cdot$ PostgreSQL $\cdot$ NestJS $\cdot$ Ionic $\cdot$ Capacitor $\cdot$ AWS $\cdot$ GPT-3}

\vspace{9pt}
\jobentry{Full Stack Engineer}{Jan 2018 -- Aug 2020}{Pawzeeble}{Mumbai}
\begin{itemize}
  \item Optimized the geospatial ``find nearest clinic'' feature, cutting infrastructure cost by \textbf{10x} while maintaining full response accuracy.
  \item Built a WYSIWYG editor with full \LaTeX{} support for clinical document authoring and in-browser file import.
  \item Delivered cross-platform apps for Android, iOS, and web from a single Ionic/Capacitor codebase.
\end{itemize}
\techstack{Angular $\cdot$ TypeScript $\cdot$ Koa $\cdot$ NestJS $\cdot$ Ionic $\cdot$ Capacitor $\cdot$ PostgreSQL}

% ── EDUCATION ────────────────────────────────────────────────────────────────
\section{Education}

\noindent
\begin{tabularx}{\linewidth}{@{}X r@{}}
  \textbf{Bachelor of Engineering, Computer Science} & \textit{2016 -- 2020} \\
  Rizvi College of Engineering, Mumbai & \\
\end{tabularx}

% ── LANGUAGES ────────────────────────────────────────────────────────────────
\section{Languages}

\noindent
\begin{tabularx}{\linewidth}{@{}X X@{}}
  \textbf{English} --- Professional & \textbf{Hindi / Urdu} --- Native \\
\end{tabularx}

\end{document}
